---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Naman Srivastava"
output: 
  rmdformats::downcute:
    self_contained: true
    lightbox: true
    gallery: false
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
library(ggthemr)
library(rmdformats)
library(AMR)
library(globe4r)
library(plotly)
```

<br><br>

## Introduction

This data comes from the Antimicrobial resistance package titled AMR, which is frequently used for epidemiological investigations. I am particularly interested in the field of antibiotic resistance and this r package contains a wide variety of suitable data that can be used for prediction analyses and data visualization.

[AMR Package](https://msberends.github.io/AMR/index.html)

```{r read-examine-data}

glimpse(microorganisms)
glimpse(antibiotics)
glimpse(example_isolates)
glimpse(WHONET)

```

<br>

## Question 1

#### Which Phylum of Fungi is most prevalent within the microorganisms dataset?

### Methods

```{r}

ggthemr("light") #Set theme
  microorganisms%>% #Main Pipe
    filter(kingdom == "Fungi")%>% #Subset data to only keep Fungi
    select(phylum)%>% #Keep only phylums
    count(phylum)%>% #Count Phylums
    ggplot()+
    aes(y=reorder(phylum, +n), #Map y-axis and reorder phylums descendingly 
        x=n, #Map counts to x-axis
        fill = phylum)+ #Fill based on phylum
    geom_col()+
    scale_x_log10()+ #Change x to a log scale
    labs(y = "Phylums", #X-axis label
         x = "Count",  #Y-axis label
         title = "Fungi Phylums examined within microorganisms dataset")+ #Add title
    theme(legend.position = "none", #Remove legend
          plot.background = element_rect(fill = "#f7f7f7")) -> Plot1 #Change background color
  ggplotly(Plot1, tooltip = c("n", "phylum")) #Change hover label to only n and phylum

```


### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### Is there a linear relationship between oral and iv dosages of antibiotics?

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### In the future, do we expect Gram-positive Bacteria to become more or less resistant to the antibiotic Doxycycline?

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### Geographically, where was the data from the WHONET dataset compiled?

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.
