---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Naman Srivastava"
output: 
  rmdformats::downcute:
    self_contained: true
    lightbox: true
    gallery: false
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
library(ggthemr)
library(rmdformats)
library(AMR)
library(globe4r)
library(plotly)
```

<br><br>

## Introduction

This data comes from the Antimicrobial resistance package titled AMR, which is frequently used for epidemiological investigations. I am particularly interested in the field of antibiotic resistance and this r package contains a wide variety of suitable data that can be used for prediction analyses and data visualization.

[AMR Package](https://msberends.github.io/AMR/index.html)

```{r read-examine-data}


```

<br><br>

## Question 1

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{r}


```


### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{r}



```


### Answer

Replace this text with your answer to your question.
